Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-05-28 manuscript/manuscript.Rmd
updates ms and adds climate sensitivity figure script

Figures
-------
```{r figure_1,cache=FALSE, results='hide'}
# resD <- readRDS("../montana/quadBM/simulations/oneStepResids_YearEffects.rds")
# resDny <- readRDS("../montana/quadBM/simulations/oneStepResids_NoYearEffects.rds")
# resD$simtype <- rep("full", nrow(resD))
# resDny$simtype <- rep("noyear", nrow(resDny))
# resDall <- rbind(resD, resDny)
# noZ <- which(resDall$lagCover!=0)
# resDall <- resDall[noZ,]
# 
# myCols <- c("#237DA4", "#7ECAD0")
# # ggplot(resDall, aes(x=resids, fill=simtype))+
# #   geom_histogram(alpha=0.5)+
# #   facet_grid(.~species, scales = "free_x")+
# #   xlab("Year")+
# #   ylab("Residuals (% cover difference)")+
# #   theme_bw()+
# #   scale_fill_manual(values=myCols)
# 
# resAgg <- ddply(resDall, .(year, species, simtype), summarise,
#                 avg_prediction = mean(cover)*100,
#                 up_prediction = quantile(cover, probs = 0.875)*100,
#                 down_prediction = quantile(cover, probs = 0.125)*100,
#                 avg_obs = mean(propCover)*100)
# resAgg$model <- rep("QBM", nrow(resAggipm))

# ggplot(subset(resAgg))+
#   geom_ribbon(aes(x=year, ymin=down_prediction, ymax=up_prediction, fill=simtype), alpha=0.3)+
#   geom_line(aes(x=year, y=avg_prediction, color=simtype), size=1.5)+
# #   geom_line(aes(x=year, y=up_prediction, color=simtype), linetype=2, alpha=0.5)+
# #   geom_line(aes(x=year, y=down_prediction, color=simtype), linetype=2, alpha=0.5)+
#   geom_point(aes(x=year, y=avg_obs), shape=1, size=3)+
#   facet_grid(species~., scales="free")+
#   scale_fill_manual(values=c(myCols[1], "darkorange"), labels=c("Year effects", "No year effects"))+
#   scale_color_manual(values=c(myCols[1], "darkorange"))+
#   guides(color=FALSE)
# nSims <- length(unique(resD$sim))
# diffD <- ddply(resDall, c("year", "species", "simtype"), summarise,
#                avgDiff = median(resids, na.rm = TRUE),
#                upDiff75 = quantile(resids, probs = 0.8775, names=FALSE, na.rm = TRUE),
#                dnDiff75 = quantile(resids, probs = 0.1225, names=FALSE, na.rm = TRUE),
#                dnDiff95 = quantile(resids, probs = 0.025, names=FALSE, na.rm = TRUE),
#                upDiff95 = quantile(resids, probs = 0.975, names=FALSE, na.rm = TRUE))

# ggplot(diffD, aes(color=simtype))+
#   geom_hline(aes(yintercept=0), linetype=2, color="grey50")+
#   geom_point(aes(x=as.character(year), y=avgDiff), size=3, position=position_dodge(width=0.5))+
#   geom_errorbar(aes(x=as.character(year), ymax=upDiff95, ymin=dnDiff95), width=0.00001, position=position_dodge(width=0.5))+
#   geom_errorbar(aes(x=as.character(year), ymax=upDiff75, ymin=dnDiff75), size=1, width=0.00001, position=position_dodge(width=0.5))+
#   facet_grid(species~., scales = "free_y")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   scale_color_manual(values=myCols)+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))
# 
# ggplot(resDall)+
#   geom_hline(aes(yintercept=0), linetype=2)+
# #   geom_line(data=diffD, aes(x=year, y=avgDiff, group=species), color="purple", alpha=0.5)+
# #   stat_smooth(data=diffD, aes(x=year, y=avgDiff, group=species), color="lightblue", se = FALSE, size=1)+
#   geom_boxplot(aes(x=year, y=resids, fill=simtype), outlier.shape = 1, width=0.3, outlier.size = 0.5)+
#   facet_grid(species~., scales = "free_y")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))
# myCols <- c("#237DA4", "#7ECAD0")
# p1 <- ggplot(subset(resDall, species=="BOGR"))+
#   geom_hline(aes(yintercept=0), linetype=2)+
#   geom_boxplot(aes(x=as.character(year), y=resids, fill=simtype), outlier.shape = 1, outlier.size = 0, color="grey25")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
#   scale_fill_manual(values=myCols)+
#   coord_cartesian(ylim = c(-50, 50))+
#   ggtitle(expression(italic("B. gracilis")))+
#   guides(fill=FALSE)
# p2 <- ggplot(subset(resDall, species=="HECO"))+
#   geom_hline(aes(yintercept=0), linetype=2)+
#   geom_boxplot(aes(x=as.character(year), y=resids, fill=simtype), outlier.shape = 1, outlier.size = 0, color="grey25")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
#   scale_fill_manual(values=myCols, labels=c("Year effects", "No year effects"))+
#   ggtitle(expression(italic("H. comita")))+
#   coord_cartesian(ylim = c(-10, 5))+
#   guides(fill=guide_legend(title=""))+
#   theme(legend.position=c(0.5,0.2))
# p3 <- ggplot(subset(resDall, species=="PASM"))+
#   geom_hline(aes(yintercept=0), linetype=2)+
#   geom_boxplot(aes(x=as.character(year), y=resids, fill=simtype), outlier.shape = 1, outlier.size = 0, color="grey25")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
#   scale_fill_manual(values=myCols)+
#   ggtitle(expression(italic("P. smithii")))+
#   guides(fill=FALSE)+
#   coord_cartesian(ylim = c(-1.5, 1.5))
# p4 <- ggplot(subset(resDall, species=="POSE"))+
#   geom_hline(aes(yintercept=0), linetype=2)+
#   geom_boxplot(aes(x=as.character(year), y=resids, fill=simtype), outlier.shape = 1, outlier.size = 0, color="grey25")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
#   scale_fill_manual(values=myCols)+
#   ggtitle(expression(italic("Poa secunda")))+
#   guides(fill=FALSE)+
#   coord_cartesian(ylim = c(-10, 15))
# pFinal <- grid.arrange(p1,p2,p3,p4, ncol=2, nrow=2)
# pFinal

```{r figure_2, dependson="plot-options", fig.cap="One step forecasts from IPM version.",fig.width=8, fig.height=8, cache=FALSE, results='hide'}
# resD <- readRDS("../montana/quadBM/simulations/oneStepResids_YearEffects.rds")
# resDny <- readRDS("../montana/quadBM/simulations/oneStepResids_NoYearEffects.rds")
# resD$simtype <- rep("full", nrow(resD))
# resDny$simtype <- rep("noyear", nrow(resDny))
# resDall <- rbind(resD, resDny)
# noZ <- which(resDall$lagCover!=0)
# resDall <- resDall[noZ,]
# 
# myCols <- c("#237DA4", "#7ECAD0")
# # ggplot(resDall, aes(x=resids, fill=simtype))+
# #   geom_histogram(alpha=0.5)+
# #   facet_grid(.~species, scales = "free_x")+
# #   xlab("Year")+
# #   ylab("Residuals (% cover difference)")+
# #   theme_bw()+
# #   scale_fill_manual(values=myCols)
# 
# resAgg <- ddply(resDall, .(year, species, simtype), summarise,
#                 avg_prediction = mean(cover)*100,
#                 up_prediction = quantile(cover, probs = 0.875)*100,
#                 down_prediction = quantile(cover, probs = 0.125)*100,
#                 avg_obs = mean(propCover)*100)
# resAgg$model <- rep("QBM", nrow(resAgg))
# 
# 
# 
# ipm_onestep <- readRDS("../montana/ipm/simulations/one_step_results/ipm_one-step_forecasts_combined.rds")
# ipm_onestep$t1 <- ipm_onestep$t1+1900
# 
# resAggipm <- ddply(ipm_onestep, .(t1, species, year), summarise,
#                 avg_prediction = mean(cover.t1)*100,
#                 up_prediction = quantile(cover.t1, probs = 0.875)*100,
#                 down_prediction = quantile(cover.t1, probs = 0.125)*100,
#                 avg_obs = mean(obs.cover.t1)*100)
# colnames(resAggipm)[1:3] <- c("year", "species", "simtype")
# resAggipm$simtype[which(resAggipm$simtype=="ayear effect")] <- "full"
# resAggipm$simtype[which(resAggipm$simtype!="full")] <- "noyear"
# resAggipm$model <- rep("IPM", nrow(resAggipm))
# 
# resAgg_both <- rbind(resAgg, resAggipm)
# 
# ggplot(subset(resAgg_both))+
#   geom_ribbon(aes(x=year, ymin=down_prediction, ymax=up_prediction, fill=simtype), alpha=0.3)+
#   geom_line(aes(x=year, y=avg_prediction, color=simtype), size=1.5)+
#   geom_point(aes(x=year, y=avg_obs), shape=1, size=3)+
#   facet_grid(species~model, scales="free")+
#   scale_fill_manual(values=c(myCols[1], "darkorange"), labels=c("Year effects", "No year effects"))+
#   scale_color_manual(values=c(myCols[1], "darkorange"))+
#   guides(color=FALSE)
# 
# ggplot(subset(resAgg_both))+
#   geom_ribbon(aes(x=year, ymin=down_prediction, ymax=up_prediction, fill=model), alpha=0.3)+
#   geom_line(aes(x=year, y=avg_prediction, color=model), size=1.5)+
#   geom_point(aes(x=year, y=avg_obs), shape=1, size=3)+
#   facet_grid(species~simtype, scales="free")+
#   scale_fill_manual(values=c(myCols[1], "darkorange"))+
#   scale_color_manual(values=c(myCols[1], "darkorange"))+
#   guides(color=FALSE)

# p1 <- ggplot(subset(ipm_onestep, species=="BOGR"))+
#   geom_hline(aes(yintercept=0), linetype=2)+
#   geom_boxplot(aes(x=as.character(t1),y=resid,fill=year), outlier.shape = 1, outlier.size = 0, color="grey25")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
#   scale_fill_manual(values=myCols)+
#   coord_cartesian(ylim = c(-50, 50))+
#   ggtitle(expression(italic("B. gracilis")))+
#   guides(fill=FALSE)
# p2 <- ggplot(subset(ipm_onestep, species=="HECO"))+
#   geom_hline(aes(yintercept=0), linetype=2)+
#   geom_boxplot(aes(x=as.character(t1),y=resid,fill=year), outlier.shape = 1, outlier.size = 0, color="grey25")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
#   scale_fill_manual(values=myCols, labels=c("Year effects", "No year effects"))+
#   ggtitle(expression(italic("H. comita")))+
#   coord_cartesian(ylim = c(-10, 5))+
#   guides(fill=guide_legend(title=""))+
#   theme(legend.position=c(0.5,0.2))
# p3 <- ggplot(subset(ipm_onestep, species=="PASM"))+
#   geom_hline(aes(yintercept=0), linetype=2)+
#   geom_boxplot(aes(x=as.character(t1),y=resid,fill=year), outlier.shape = 1, outlier.size = 0, color="grey25")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
#   scale_fill_manual(values=myCols)+
#   ggtitle(expression(italic("P. smithii")))+
#   guides(fill=FALSE)+
#   coord_cartesian(ylim = c(-1.5, 1.5))
# p4 <- ggplot(subset(ipm_onestep, species=="POSE"))+
#   geom_hline(aes(yintercept=0), linetype=2)+
#   geom_boxplot(aes(x=as.character(t1),y=resid,fill=year), outlier.shape = 1, outlier.size = 0, color="grey25")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
#   scale_fill_manual(values=myCols)+
#   ggtitle(expression(italic("Poa secunda")))+
#   guides(fill=FALSE)+
#   coord_cartesian(ylim = c(-10, 15))
# pFinal <- grid.arrange(p1,p2,p3,p4, ncol=2, nrow=2)
# pFinal
```

```{r figure_3, dependson="plot-options", fig.cap="One step forecasts from IPM version.",fig.width=8, fig.height=8, cache=FALSE, results='hide', eval=FALSE}
# ipm_onestep2 <- subset(ipm_onestep, year=="ayear effect")
# resDall2 <- subset(resDall, simtype=="full")
# ipm_qbm_onestep <- data.frame(year = c(ipm_onestep2$t1, resDall2$year),
#                               resids = c(ipm_onestep2$resid, resDall2$resids),
#                               model = c(rep("IPM", nrow(ipm_onestep2)),
#                                         rep("QBM", nrow(resDall2))),
#                               species = c(ipm_onestep2$species, resDall2$species))
# g1 <- ggplot(subset(ipm_qbm_onestep, species=="BOGR"))+
#   geom_hline(aes(yintercept=0), linetype=2)+
#   geom_boxplot(aes(x=as.character(year),y=resids,fill=model), outlier.shape = 1, outlier.size = 0, color="grey25")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
#   scale_fill_manual(values=myCols)+
#   coord_cartesian(ylim = c(-50, 50))+
#   ggtitle(expression(italic("B. gracilis")))+
#   guides(fill=FALSE)
# g2 <- ggplot(subset(ipm_qbm_onestep, species=="HECO"))+
#   geom_hline(aes(yintercept=0), linetype=2)+
#   geom_boxplot(aes(x=as.character(year),y=resids,fill=model), outlier.shape = 1, outlier.size = 0, color="grey25")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
#   scale_fill_manual(values=myCols)+
#   coord_cartesian(ylim = c(-10, 5))+
#   ggtitle(expression(italic("H. comata")))+
#   guides(fill=guide_legend(title=""))+
#   theme(legend.position=c(0.5,0.2))
# g3 <- ggplot(subset(ipm_qbm_onestep, species=="PASM"))+
#   geom_hline(aes(yintercept=0), linetype=2)+
#   geom_boxplot(aes(x=as.character(year),y=resids,fill=model), outlier.shape = 1, outlier.size = 0, color="grey25")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
#   scale_fill_manual(values=myCols)+
#   ggtitle(expression(italic("P. smithii")))+
#   guides(fill=FALSE)+
#   coord_cartesian(ylim = c(-1.5, 1.5))
# g4 <- ggplot(subset(ipm_qbm_onestep, species=="POSE"))+
#   geom_hline(aes(yintercept=0), linetype=2)+
#   geom_boxplot(aes(x=as.character(year),y=resids,fill=model), outlier.shape = 1, outlier.size = 0, color="grey25")+
#   xlab("Year")+
#   ylab("Residuals (% cover difference)")+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))+
#   scale_fill_manual(values=myCols)+
#   ggtitle(expression(italic("Poa secunda")))+
#   coord_cartesian(ylim = c(-10, 15))+
#   guides(fill=FALSE)
# pFinal <- grid.arrange(g1,g2,g3,g4, ncol=2, nrow=2)
# pFinal
```

```{r ipm_climeffs, cache=FALSE, results='hide', include=FALSE}
source("../montana/ipm/vitalRateRegs/climate_effects_plots.R")
```

![Standardized regression coefficients for climate effects in the vital rate models for the IPM. Shown are the median (circles), 75% confidence intervals (thick lines), and 95% confidence intervals (thin lines). Left panels (black) are for the growth regressions; middle panels (blue) are for the survival regressions; right panels (orange) are for the recruitment regressions.](components/figure/ipm_climeffs.pdf)

```{r quad_climeffs, cache=FALSE, results='hide', include=FALSE}
source("../montana/quadBM/vitalRateRegressions/truncNormModel/climate_effects_plot.R")
```

![Standardized regression coefficients for climate effects in the vital rate models for the QBM. Shown are the median (circles), 75% confidence intervals (thick lines), and 95% confidence intervals (thin lines).](components/figure/qbm_climeffs.pdf)

```{r figure_4, dependson="plot-options", fig.cap="Proportional change in species' mean cover caused by a 1% increase in observed precipitation, temperature, or both as predicted by the individual-based IPM and the aggregate-based QBM. Note that the change for POSE due to a precipitation increase predicted by the QBM is almost zero and so does not show up in the figure. Labels on x-axis refer to: 'ppt' = 1% increase in mean precipitation; 'temp' = 1% increase in mean temperature; 'ppt + temp' = 1% increase in mean precipitation and mean temperature.", fig.width=6.5, fig.height=6, cache=FALSE, results='hide'}
qbm_diffs <- readRDS("../montana/quadBM/simulations/results/qbm_climatesims_percdiffs.rds")
qbm_diffs$type <- rep("QBM", nrow(qbm_diffs))
ipm_diffs <- readRDS("../montana/ipm/simulations/results/ipm_climatesims_percdiffs.rds")
ipm_diffs$type <- rep("IPM", nrow(ipm_diffs))

>>>>

Figures
-------

```{r ipm_climeffs, cache=FALSE, results='hide', include=FALSE}
# source("../montana/ipm/vitalRateRegs/climate_effects_plots.R")
# ![Standardized regression coefficients for climate effects in the vital rate models for the IPM. Shown are the median (circles), 75% confidence intervals (thick lines), and 95% confidence intervals (thin lines). Left panels (black) are for the growth regressions; middle panels (blue) are for the survival regressions; right panels (orange) are for the recruitment regressions.](components/figure/ipm_climeffs.pdf)
```

```{r quad_climeffs, cache=FALSE, results='hide', include=FALSE}
# source("../montana/quadBM/vitalRateRegressions/truncNormModel/climate_effects_plot.R")
# ![Standardized regression coefficients for climate effects in the vital rate models for the QBM. Shown are the median (circles), 75% confidence intervals (thick lines), and 95% confidence intervals (thin lines).](components/figure/qbm_climeffs.pdf)
```

```{r figure_1, dependson="plot-options", fig.cap="Sensitivity of equilibrium cover to removal of climate effects from each vital rate regression.", fig.width=4.5, fig.height=6, cache=FALSE, results='hide'}
setwd("../montana/ipm/simulations/sensitivity_results/")
files <- list.files()
cover_files <- files[grep("cover", files)]
spp_id <- substr(cover_files, 1, 4)
clim_id <- rep(c("allClim", "noPpt", "noTemp",
                 "noPpt", "noTemp",
                 "noPpt", "noTemp"), 4)
vital_id <- rep(c("All", "Growth", "Growth",
                  "Survival", "Survival",
                  "Recruitment", "Recruitment"), 4)
num_files <- length(cover_files)
all_sims <- data.frame(time=NA, cover=NA, species=NA, sim=NA, vital=NA)
for(i in 1:num_files){
  tmp <- read.csv(cover_files[i])
  tmp$species <- rep(spp_id[i], nrow(tmp))
  tmp$sim <- rep(clim_id[i], nrow(tmp))
  tmp$vital <- rep(vital_id[i], nrow(tmp))
  all_sims <- rbind(all_sims, tmp)
}
all_sims <- all_sims[2:nrow(all_sims),]
all_clim_sims <- subset(all_sims, vital=="All")

species <- unique(all_sims$species)
vital_adds <- c("Growth", "Survival", "Recruitment") 
out_controls <- data.frame(time=NA, cover=NA, species=NA, sim=NA, vital=NA)
for(spp in species){
  tmp <- subset(all_clim_sims, species==spp)
  for(vital in vital_adds){
    tmp$vital <- vital
    out_controls <- rbind(out_controls, tmp)
  }
}
out_controls <- out_controls[2:nrow(out_controls),]

all_noclim_sims <- subset(all_sims, vital!="All")
final <- rbind(out_controls, all_noclim_sims)

equilibrium_cover <- ddply(final, .(species, sim, vital), summarise,
                           eq_cover = median(cover))

mean_cover <- ddply(subset(equilibrium_cover, sim=="allClim"), .(species), summarise,
                    value = mean(eq_cover))

myCols2 <- c("#277BA8", "#7ABBBD", "#AED77A")
ggplot(equilibrium_cover, aes(x=sim, y=eq_cover*100, 
                              linetype=vital, group=vital, shape=vital))+
  geom_hline(data=mean_cover, aes(yintercept=value*100), linetype=2, color="grey45")+
  geom_line()+
  geom_point(size=4)+
  facet_grid(species~., scales = "free")+
  scale_linetype_manual(values=c(1,2,3), name="Vital Rate")+
  scale_shape_manual(values=c(19,17,15), name="Vital Rate")+
  ylab("Equilibrium Cover (%)")+
  xlab("Simulation")+
  theme_bw()
setwd("~/Repos/MicroMesoForecast/manuscript")
```

```{r figure_2, dependson="plot-options", fig.cap="Proportional change in species' mean cover caused by a 1% increase in observed precipitation, temperature, or both as predicted by the individual-based IPM and the aggregate-based QBM. Note that the change for POSE due to a precipitation increase predicted by the QBM is almost zero and so does not show up in the figure. Labels on x-axis refer to: 'ppt' = 1% increase in mean precipitation; 'temp' = 1% increase in mean temperature; 'ppt + temp' = 1% increase in mean precipitation and mean temperature.", fig.width=6.5, fig.height=6, cache=FALSE, results='hide'}
qbm_diffs <- readRDS("../montana/quadBM/simulations/results/qbm_climatesims_percdiffs.rds")
qbm_diffs$type <- rep("QBM", nrow(qbm_diffs))
ipm_diffs <- readRDS("../montana/ipm/simulations/results/ipm_climatesims_percdiffs.rds")
ipm_diffs$type <- rep("IPM", nrow(ipm_diffs))

### 2015-05-28 manuscript/manuscript.tex
updates ms and adds climate sensitivity figure script

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Climate detection
\item
  Limitations:
\end{enumerate}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Sample size at quadrat level
\item
  are these species inherently sensitive to climate (compare to Chu and
  Adler in review -- say why we chose Montana site -- most sensitive to
  climate variables)
\item
  we know recruitment is important, and this is something that may be
  easily missed at quad level
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Implications
\end{enumerate}

@@

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/ipm_climeffs.pdf}
\caption{Standardized regression coefficients for climate effects in the
vital rate models for the IPM. Shown are the median (circles), 75\%
confidence intervals (thick lines), and 95\% confidence intervals (thin
lines). Left panels (black) are for the growth regressions; middle
panels (blue) are for the survival regressions; right panels (orange)
are for the recruitment regressions.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/qbm_climeffs.pdf}
\caption{Standardized regression coefficients for climate effects in the
vital rate models for the QBM. Shown are the median (circles), 75\%
confidence intervals (thick lines), and 95\% confidence intervals (thin
lines).}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_4.pdf}
\caption{Proportional change in species' mean cover caused by a 1\%
increase in observed precipitation, temperature, or both as predicted by
the individual-based IPM and the aggregate-based QBM. Note that the
change for POSE due to a precipitation increase predicted by the QBM is
almost zero and so does not show up in the figure. Labels on x-axis
refer to: `ppt' = 1\% increase in mean precipitation; `temp' = 1\%
increase in mean temperature; `ppt + temp' = 1\% increase in mean
precipitation and mean temperature.}
\end{figure}

>>>>

@@

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_1.pdf}
\caption{Sensitivity of equilibrium cover to removal of climate effects
from each vital rate regression.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_2.pdf}
\caption{Proportional change in species' mean cover caused by a 1\%
increase in observed precipitation, temperature, or both as predicted by
the individual-based IPM and the aggregate-based QBM. Note that the
change for POSE due to a precipitation increase predicted by the QBM is
almost zero and so does not show up in the figure. Labels on x-axis
refer to: `ppt' = 1\% increase in mean precipitation; `temp' = 1\%
increase in mean temperature; `ppt + temp' = 1\% increase in mean
precipitation and mean temperature.}
\end{figure}
